\mytitle

### 2016-11-04 paper.tex
paper.tex - add acknowledgments
paper.tex - minor reformulation in conclusion/outlook part

We presented our submission to the PoSTWITA ST, where we participated
with moderate results. 
In the future, we will try to rerun the experiment with training data that
takes into consideration the Twitter-specific tags of the ST.

%\section*{Acknowledgments} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The acknowledgments should go immediately before the references.  Do
%not number the acknowledgments section. Do not include this section
%when submitting your paper for review.

>>>>

We presented our submission to the PoSTWITA task of EVALITA 2016, where we
participated with moderate results. 
In the future, we will try to rerun the experiment with training data that
takes into consideration the Twitter-specific tags of the task.

\section*{Acknowledgments} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The computational results presented have been achieved in part using the Vienna
Scientific Cluster (VSC).
